\bf Title

### 2023-10-25 article/paper_padic_spec.tex
corrected p-adic linear programming

\begin{definition}
	We call {\it convex $p$-adic polyhedra} subsets of $K^s$ defined by linear inequalities $\val\left( \ell_1(x)\right)\ge 0$,\ldots, $ \val\left( \ell_n\left( x \right) \right)\ge 0$ for $ \ell_1,\ldots, \ell_n $ fixed linear forms and for all $x \in K ^s$.

@@

\subsection{linear programming}
	We call { \it $p$-adic programming} the problem :
\begin{equation}
	\tag{PLp}
	\begin{matrix}
		\text{Minimize } \val\left(\left<c,x \right>\right) \text{ subject to }\\
		Ax + b \ge 0
	\end{matrix}
	\label{eqn:Proglinp}
\end{equation}

with $x$ a vector of $K ^n$, and $c$ a fixed vector of size $n$ that represents the cost, $A$ a fixed $m \times n $ matrix and $b$ fiexed a vector of size $m$.

@@

	We call {\it Smith normal form} of a matrix $M \in \mathcal{M}_{m,n}\left(K \right) $ of rank $r$ the only matrix $S$ of the form $$S =  
	\begin{pmatrix} p^{a_1} & \\
		& \ddots \\
		& & p^{ar}\\
		& & & 0\\
		& & & & \ddots \end{pmatrix} $$
	so that $(a_1)_{1\le i\le r}$ is a increasing sequence of integers and $M$ can be written $M =  Q^{-1} S P$ for $P \in \mathcal{G}L_n\left( \OK \right) $, $Q \in \mathcal{G}L_m\left( \OK \right) $.
\end{definition}

\begin{remark}
	\begin{enumerate}%[label=\roman*.]
		\item The coefficient of the Smith normal Form are unique and called \textit{invariant factors}.
		\item The $p$-adic valuation of the first coefficient of the Smith normal form of a matrix $M \in \mathcal{M}_n \left( K \right) $ is the minimum of the valuations of the matrix $M$'s terms.
		\item In particular, the the normal Smith form of matrix of $\mathcal{M}_n \left( \OK \right) $ have coefficients in $\OK$ .
		\item The $r = \text{rank} M$ first diagonals coefficients of $S$ are exactly its non-zero coefficient.
	\end{enumerate}

@@

\begin{lemma}
	Forall $p$-adic numbers $z \in K ^n$ and matrix $M \in \mathcal{M}_{m,n}\left( K  \right)  $ if $z\ge 0$ and $M\ge 0$ then $Mz\ge 0$.  
\end{lemma}
\begin{proof}
	$\OK$ is a ring.
\end{proof}

@@

\begin{equation}
	\tag{PLp'}
	\begin{matrix}
		\text{Minimize } \val\left(\left<c',x \right>\right) \text{ subject to }\\
		Sy + b' \ge 0
	\end{matrix}
	\label{eqn:Proglinp2}
\end{equation}
where $b' = Qb$, $c' = P^Tc$, $S$ is the Smith normal form of $A$ and $A = Q^{-1} S P$ for some $P \in \mathcal{G}L_m\left( \OK \right)$ and $ Q \in \mathcal{G}L_n\left( \OK \right)$.

@@

\end{itemize}
\begin{remark}
	To maximize the valuation of a linear map over a convex $p$-adic polyhedron instead of minimizing it (which is equuivalent to minimize the absolute value) the same reasoning can be apllied. The only differnece being that if $\val\left( \lambda\right) < v$ the problem is unbounded and then does not have any solution. 
\end{remark}

@@

	A matrixe is positive semidefinite if and only if its characteristic polynomial have coefficients in $\OK$ .

@@

\textit{Preuve : }  $\OK$ is a ring therefore the characteristic polynomial of matrix whose coefficients are $p$-adic integers have coefficients ins $Pp$. We conclude by \ref{caracsdp} .

\begin{remark}
	In general, the reciprocal inclusion is false [not sure about this one]. For instance the characteristic polynomial of $M = \begin{pmatrix} 5 + \frac{3}{5} & \frac{4}{5} \\ \frac{4}{5} & -\frac{3}{5} \end{pmatrix} $ is $\chi_M = X^2  - 5 X - 4$. However when seen as an element of $\mathbb{Q}_5$, $\chi_M \in \mathbb{Z}_5[X]$ then $M \in \mathcal{M}_2^+\left( \mathbb{Q}_5 \right)$ but no coefficient of $M$ is in $\mathbb{Z}_5 $
\end{remark}

@@

\begin{definition}
	We call {\it $p$-adic spectrahedron} the intersection of $\mathcal{M}_n^+\left( K \right) $ with an affine plan $\mathcal{L}$ of $\mathcal{M}_n\left( K \right) $.
\end{definition}

@@

The latter allows gives us the following property :
\begin{proposition}
	A convex $p$-adic polyhedron is $p$-adic spectrahedron.
\end{proposition}
\begin{proof}
	Same as in the real case (maybe modify it or add the link to real proof).
\end{proof}

>>>>

\begin{definition}
	We call {\it polyhedra} subsets of $K^s$ defined by linear inequalities $\val\left( \ell_1(x)\right)\ge 0$,\ldots, $ \val\left( \ell_n\left( x \right) \right)\ge 0$ for $ \ell_1,\ldots, \ell_n $ fixed linear forms and for all $x \in K ^s$.

@@

\subsection{linear programming}
	We call { \it $p$-adic linear programming} the problem :
\begin{equation}
	\tag{PLp}
	\begin{matrix}
		\text{Minimize } \val\left(\left<c,x \right>\right) \text{ subject to }\\
		Ax + b \ge 0
	\end{matrix}
	\label{eqn:Proglinp}
\end{equation}

with $x$ a vector of $K ^n$, and $c$ a fixed vector of size $n$ that represents the cost, $A$ a fixed $m \times n $ matrix and $b$ fixed a vector of size $m$.

@@

	We call {\it Smith normal form} of a matrix $M \in \mathcal{M}_{m,n}\left(K \right) $ of rank $r$ the only matrix $S$ of the form $$S =  
	\begin{pmatrix} p^{a_1} & \\
		& \ddots \\
		& & p^{a_r}\\
		& & & 0\\
		& & & & \ddots \end{pmatrix} $$
	so that $(a_1)_{1\le i\le r}$ is a increasing sequence of integers and $M$ can be written $M =  Q^{-1} S P$ for $P \in \mathcal{G}L_n\left( \ZZ_p \right) $, $Q \in \mathcal{G}L_m\left( \ZZ_p \right) $.
\end{definition}

\begin{remark}
	\begin{enumerate}%[label=\roman*.]
		\item The coefficient of the Smith normal form are unique and called \textit{invariant factors}.
		\item The valuation of the first coefficient of the Smith normal form of a matrix $M \in \mathcal{M}_n \left( \QQ_p \right) $ is the minimum of the valuations of the matrix $M$'s terms.
		\item In particular, the the normal Smith form of matrix of $\mathcal{M}_n \left( \OK \right) $ have coefficients in $\ZZ_p$ .
		\item The $r = \text{rank} M$ first diagonals coefficients of $S$ are exactly its non-zero coefficient.
	\end{enumerate}

@@

\begin{lemma}
	Forall $p$-adic numbers $z \in \QQ_p ^n$ and matrix $M \in \mathcal{M}_{m,n}\left( \QQ_p  \right)  $ if $z\ge 0$ and $M\ge 0$ then $Mz\ge 0$.  
\end{lemma}
\begin{proof}
	$\ZZ_p$ is a ring.
\end{proof}

@@

\begin{equation}
	\tag{PLp'}
	\begin{matrix}
		\text{Minimize } \val\left(\left<c',x \right>\right) \text{ subject to }\\
		Sy + b' \ge 0
	\end{matrix}
	\label{eqn:Proglinp2}
\end{equation}
where $b' = Qb$, $c' = P^Tc$, $S$ is the Smith normal form of $A$ and $A = Q^{-1} S P$ for some $P \in \mathcal{G}L_m\left( \ZZ_p \right)$ and $ Q \in \mathcal{G}L_n\left( \ZZ_p \right)$.

@@

\end{itemize}
\begin{remark}
	To maximize the valuation of a linear map over a convex $p$-adic polyhedron instead of minimizing it (which is equuivalent to minimize the absolute value) the same reasoning can be aplied. The only differnece being that if $\val\left( \lambda\right) < v$ the problem is unbounded and then does not have any solution. 
\end{remark}

@@

	A matrix is positive semidefinite if and only if its characteristic polynomial have coefficients in $\OK$ .

@@

\begin{proof}
$\OK$ is a ring therefore the characteristic polynomial of matrix whose coefficients are $p$-adic integers have coefficients ins $Pp$. We conclude by \ref{caracsdp} .
\end{proof}

\begin{remark}
	In general, the reverse inclusion is false. For instance the characteristic polynomial of $M = \begin{pmatrix} 5 + \frac{3}{5} & \frac{4}{5} \\ \frac{4}{5} & -\frac{3}{5} \end{pmatrix} $ is $\chi_M = X^2  - 5 X - 4$. However when seen as an element of $\mathbb{Q}_5$, $\chi_M \in \mathbb{Z}_5[X]$ then $M \in \mathcal{M}_2^+\left( \mathbb{Q}_5 \right)$ but no coefficient of $M$ is in $\mathbb{Z}_5 $
\end{remark}

@@

\begin{definition}
	We call {\it spectrahedron} the intersection of $\mathcal{M}_n^+\left( K \right) $ with an affine plan $\mathcal{L}$ of $\mathcal{M}_n\left( K \right) $.
\end{definition}

@@

The latter allows gives us the following property :
\begin{proposition}
	A polyhedron is a spectrahedron.
\end{proposition}
\begin{proof}
	Same as in the real case (maybe modify it or add the link to real proof).
\end{proof}
